Hydra Battles and Cie

### 2021-08-23 doc/part-hydras.tex
conversion to Alectryon (chapter 5, more than half done)

\begin{Coqsrc}
Corollary Cor12 (alpha : T1) :  nf alpha ->
         forall beta i n, beta  t1< alpha  ->
                i < n ->
                 const_pathS i alpha beta ->
                 const_pathS n alpha beta.
Proof.
  transfinite_induction_lt alpha.
  (* (long) proof skipped *)
\end{Coqsrc}

@@

\begin{Coqsrc}
Corollary Cor12_1 (alpha : T1) :
  nf alpha ->
  forall beta i n, beta t1< alpha ->
                   i <= n ->
                   const_pathS i alpha beta ->
                   const_pathS n alpha beta.
\end{Coqsrc}

>>>>

\emph{From
  Module~\href{../theories/html/hydras.Epsilon0.Paths.html}{Epsilon0.Paths}}

\input{movies/snippets/Paths/Cor12}

@@

\input{movies/snippets/Paths/Cor121}
